### 2024-06-24 basic-statistics.qmd
20240624 - repeated measures ANOVA

```{r}
library("petersenlab")
library("pwr")
library("grid")
library("tidyverse")
```

@@

$$
\begin{aligned}
  R^2 &= 1 - \frac{\sum (Y_i - \hat{Y}_i)^2}{\sum (Y_i - \bar{Y})^2} \\
      &= 1 - \frac{SS_{\text{residual}}}{SS_{\text{total}}} \\
      &= 1 - \frac{\text{sum of squared residuals}}{\text{total sum of squares}}
\end{aligned}
$$ {#eq-rSquared}

@@

```{r}
alpha <- .05
N <- 200
nGroup1 <- 150
nGroup2 <- 150
numGroups <- 4
numLevelsFactorA <- 3
numLevelsFactorB <- 4
numTimepoints <- 4
numPredictors <- 5
numCategories <- 6
numRows <- 5
numColumns <- 2
```

@@

where $N$ is sample size and $T$ is the number of timepoints (or conditions).

```{r}
df1_RMANOVA <- numTimepoints - 1
df2_RMANOVA <- (numTimepoints - 1) * (N - 1)
```

@@

@@

@@

>>>>

```{r}
library("petersenlab")
library("pwr")
library("WebPower")
library("grid")
library("tidyverse")
```

@@

$$
\begin{aligned}
  R^2 &= 1 - \frac{\sum (Y_i - \hat{Y}_i)^2}{\sum (Y_i - \bar{Y})^2} \\
      &= 1 - \frac{SS_{\text{residual}}}{SS_{\text{total}}} \\
      &= 1 - \frac{\text{sum of squared residuals}}{\text{total sum of squares}} \\
      &= \frac{f^2}{1 + f^2}
\end{aligned}
$$ {#eq-rSquared}

@@

```{r}
alpha <- .05
N <- 200
nGroup1 <- 150
nGroup2 <- 150
numGroups <- 4
numLevelsFactorA <- 3
numLevelsFactorB <- 4
numMeasurements <- 4
numPredictors <- 5
numCategories <- 6
numRows <- 5
numColumns <- 2
```

@@

where $N$ is sample size and $T$ is the number of measurements (i.e., the number of levels of the within-person factor: e.g., timepoints or conditions).

```{r}
df1_RMANOVA <- numMeasurements - 1
df2_RMANOVA <- (numMeasurements - 1) * (N - 1)
```

@@

```{r}
wp.rmanova(
  n = N,
  ng = numGroups,
  nm = numMeasurements,
  f = effectSize_f,
  alpha = alpha,
  type = 0)

wp.rmanova(
  n = N,
  ng = numGroups,
  nm = numMeasurements,
  f = effectSize_f,
  alpha = alpha,
  type = 1)

wp.rmanova(
  n = N,
  ng = numGroups,
  nm = numMeasurements,
  f = effectSize_f,
  alpha = alpha,
  type = 2)
```

@@

```{r}
wp.rmanova(
  power = power,
  ng = numGroups,
  nm = numMeasurements,
  f = effectSize_f,
  alpha = alpha,
  type = 0)

wp.rmanova(
  power = power,
  ng = numGroups,
  nm = numMeasurements,
  f = effectSize_f,
  alpha = alpha,
  type = 1)

wp.rmanova(
  power = power,
  ng = numGroups,
  nm = numMeasurements,
  f = effectSize_f,
  alpha = alpha,
  type = 2)
```

@@

```{r}
wp.rmanova(
  n = N,
  ng = numGroups,
  nm = numMeasurements,
  power = power,
  alpha = alpha,
  type = 0)

wp.rmanova(
  n = N,
  ng = numGroups,
  nm = numMeasurements,
  power = power,
  alpha = alpha,
  type = 1)

wp.rmanova(
  n = N,
  ng = numGroups,
  nm = numMeasurements,
  power = power,
  alpha = alpha,
  type = 2)
```
